Trustability of certification systems

### 2015-12-22 paper.tex
Begining DANE

DANE is not implemented yet, but a IETF team is working on the standard.

@@

>>>>

DANE is not implemented yet, but a IETF team is working on the standard.\\
It has begin with a simple assert: why use a new trust infrastructure if we already have to use DNS to resolve a domain name?\\
From here, DNS must be securised, knowing that it is easily to set a MITM with DNS cache poisoning \cite{bor08} \cite{aa04}. That is the main purpose of DNSSEC: secure DNS. DANE allow to store keys in DNS. Thereby, \verb$www.example.org$ would be able to secure \verb$https://www.example.org$ without using a suspicious third part, just by putting its keys in the domain name that it controls. By its arborescent nature, \verb$example.org$ shall not be able to cheat on \verb$example.com$.

@@

\bibitem{bor08} Stéphane Bortzmeyer. Comment fonctionne la faille kaminsky ? http://www.bortzmeyer.org/comment-fonctionne-la-faille-kaminsky.html, 2008.

\bibitem{aa04} D. Atkins and R. Austein. Rfc 3833 : Threat analysis of the domain name system (dns). http://www.
ietf.org/rfc/rfc3833.txt, 2004.
